The Shape Matching Element Method: Direct Animation of Curved Surface Models

### 2021-04-09 paper/sections/results.tex
shtuff

We also show that our raycasting weight computation is able to create shape-aware output. \reffig{independence} and \reffig{octopus} show that manipulating
parts that are nearby but separated will behave in an appropriately independent fashion. Our grumpy model is capable of extending 
its leg without causing unrealistic deformations in the plant foot, and our octopus model shows independent motion of all eight limbs upon contact with the ground.

>>>>

We also show that our raycasting weight computation is able to create shape-aware output. \reffig{independence} and \revise{\reffig{octopus} show that manipulating
parts that are nearby but separated will behave in an appropriately independent fashion. Our grumpy model is capable of extending 
its leg without causing unrealistic deformations in the plant foot, and our octopus model shows independent motion of all eight limbs upon contact with the ground.}
